The Galactic Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-04-16 paper/ms.tex
Update numbers in plot for deltaphi plot

From Figure~\ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor{} horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi/\pi > 0.036, 0.047,
0.10\,\text{rad}$, with corresponding physical scales of $\lambda \sim 465,
610, 1290\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. These can be
considered estimates of the range of validity for an extension of the locally
determined axisymmetric coordinate system, at least when it comes to the study
of stars on quasi-circular orbits.

@@

\begin{figure}
\plotone{fig/cluster_offset.pdf}
\caption{The $z$ offset necessary in order for the action error induced by our
midplane effect to be comparable to the intrinsic action dispersion from a
cluster of mass $m_c$. We compute the intrinsic dispersion from
Equation~\ref{eq:action_disp} and convert the dispersion to a $z$ offset using
the result from Figure~\ref{fig:many_orbit_wrong_ref}. We consider the result
for the thin and thick orbit (Table~\ref{tab:orbits}). Nearby open clusters
(Table~\ref{tab:real_clusters}) have orbits closest to the thin orbit .}
\label{fig:cluster_offset}
\end{figure}

>>>>

From Figure~\ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor{} horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi/\pi > 0.072, 0.11,
0.34\,\text{rad}$, with corresponding physical scales of $\lambda \sim 900,
1400, 4300\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. These can be
considered estimates of the range of validity for an extension of the locally
determined axisymmetric coordinate system, at least when it comes to the study
of stars on quasi-circular orbits.

@@

\begin{figure}
\plotone{fig/cluster_offset.pdf}
\caption{The $z$ offset necessary in order for the action error induced by our
midplane effect to be comparable to the intrinsic action dispersion from a
cluster of mass $m_c$. We compute the intrinsic dispersion from
Equation~\ref{eq:action_disp} and convert the dispersion to a $z$ offset using
the result from Figure~\ref{fig:many_orbit_wrong_ref}. We consider the result
for the thin and thick orbit (Table~\ref{tab:orbits}). Nearby open clusters
(Table~\ref{tab:real_clusters}) have orbits closest to the thin orbit.}
\label{fig:cluster_offset}
\end{figure}
